The influence of massive early merger events on the chemo-dynamics of galaxy discs

### 2022-10-21 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/279e12_merger_ratio_gas.pdf}
        \caption{Gas mass (blue line, left axis) and merger ratio (orange line, right axis) as a function of time. We identify gas rich mergers that contribute around 10\% of gas to the main galaxy between times of 2-4 Gyr and a late time merger starting around 9.5 Gyr that contributes 10\% of gas and continues for several pericenter passages and goes on for $\sim2$ Gyr.
        }
        \label{fig:merger_ratio}
    \end{centering}
\end{figure}

\begin{figure}
    \script{half_mass_radius_metal_gradient.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/half_mass_radius_metal_gradient.pdf}
        \caption{
            Half mass radius of the cold gas (orange line, right axis) and the metallicity gradient (blue line, left axis) as a function of time. The sharp increases in the cold gas size around the times of gas rich mergers coincide with a sudden steepening of the metallicity gradient of $\sim0.02$ dex/kpc. The addition of relatively unenriched cold gas by the merging satellite leads to a sudden increase of the star-forming cold gas  mass in the outskirts of the galaxies while the central parts are unaffected. This steepens the gradient.
        }
        \label{fig:half_mass}
    \end{centering}
\end{figure}

>>>>

\begin{figure*}
    \script{merger_ratios.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/merger_ratios.pdf}
        \caption{Gas mass (blue line, left axis) and merger ratio (orange line, right axis) as a function of time. We identify several gas rich mergers that contribute around 10\% of gas to the main galaxy at various times of 2-4 Gyr and a late time merger starting around 9.5 Gyr that contributes 10\% of gas and continues for several pericenter passages and goes on for $\sim2$ Gyr.
        }
        \label{fig:merger_ratio}
    \end{centering}
\end{figure*}

\begin{figure*}
    \script{half_mass_radius_metal_gradient.py}
    \begin{centering}
     \includegraphics[width=\linewidth]{figures/half_mass_radius_metal_gradient.pdf}
        \caption{
            Half mass radius of the cold gas (orange line, right axis) and the metallicity gradient (blue line, left axis) as a function of time. The sharp increases in the cold gas size around the times of gas rich mergers coincide with a sudden steepening of the metallicity gradient of $\sim0.02$ dex/kpc. The addition of relatively unenriched cold gas by the merging satellite leads to a sudden increase of the star-forming cold gas  mass in the outskirts of the galaxies while the central parts are unaffected. This steepens the gradient.
        }
        \label{fig:half_mass}
    \end{centering}
\end{figure*}
